Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-16 treestats_paper.tex
branch length units?

\begin{figure}
    \includegraphics{{figures/1kg/relate_chr20.site.1000000.region.diversity}.pdf}
    \includegraphics{{figures/1kg/relate_chr20.branch.1000000.region.diversity}.pdf}
    \caption{
        \textbf{(top)} Mean sequence diversity
        in 1Mb windows along human chromosome 20 of the 1000 Genomes Project,
        and \textbf{(bottom)}
        the dual branch statistic as calculated from tree sequences inferred by Relate~\citep{speidel2019method}.
        Separate curves are plotted for each sampling location.
        \label{fig:chr20}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics{{figures/1kg/relate_chr20.site.1000000.region.diversity}.pdf}
    \includegraphics{{figures/1kg/relate_chr20.branch.1000000.region.diversity}.pdf}
    \caption{
        \textbf{(top)} Mean sequence diversity
        in 1Mb windows along human chromosome 20 of the 1000 Genomes Project,
        in units of mean number of pairwise differences per nucleotide,
        and \textbf{(bottom)}
        the dual branch statistic as calculated from tree sequences inferred by Relate~\citep{speidel2019method},
        in units of generations \plr{XXX confirm this}.
        Separate curves are plotted for each sampling location.
        Note that the Site statistic divided by the Branch statistic is close to $2 \times 10^{-8}$,
        the mutation rate used by Relate \plr{XXX total speculation here}.
        \label{fig:chr20}
    }
\end{figure}
